Attract and kill: Spinosad containing spheres to control onion maggot (\textit{Delia antiqua})

### 2020-01-06 manuscript/pest-management-science/reviewer-response/reviewer-response.tex

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{changepage}% http://ctan.org/pkg/changepage
\usepackage{float}
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage{graphicx}
\usepackage{ragged2e}
\usepackage{scrextend}
\usepackage{lastpage}
\usepackage{geometry}
 \geometry{
 left = 1.5in,
 right = 1.5in,
 top = 1in
 }
\pagestyle{fancy}
\renewcommand{\headrulewidth}{0pt}
\rhead{\includegraphics[height= 1cm]{ento1.png}\vspace{1em}}
\chead{\includegraphics[width = 5cm]{agritech1.png}}
\lhead{\includegraphics[width=3cm]{acet1.png}}

\fancyfoot{}
\setlength\headheight{40.8pt}
\RequirePackage[colorlinks=true, allcolors=blue]{hyperref}
\usepackage{titlesec}
\titleformat{\section}{\normalfont\fontsize{10}{15}\bfseries}{\thesection}{0em}{}
\titlespacing{\section}{}{1.24em}{0.24em}

\usepackage[default]{lato}
\usepackage[T1]{fontenc}

\cfoot{Page \thepage \hspace{1pt} of \pageref{LastPage}}

\begin{document}

\begin{addmargin}[3.8in]{}
Willett, Filgueiras, \newline
Nyrop and Nault \newline
----------------------------- \newline
Denis S. Willett\newline
Department of Entomology \newline
Cornell AgriTech  \newline
Cornell University \newline
15 Castle Creek Drive \newline
Geneva, NY 14456 \newline
deniswillett@cornell.edu \newline
\end{addmargin}
\setlength{\parindent}{0cm}

December 24, 2019

\vspace{1.24em}

Journal of Applied Entomology

\vspace{1.24em}

Dear Prof. Stefan Vidal,

\vspace{0.48em}
\setlength{\parindent}{1.24cm}

Thank you for your consideration of \textit{“Field monitoring of Onion Maggot (\textit{Delia antiqua}) fly through improved trapping”} for publication in the Journal of Applied Entomology.  We have revised the manuscript in accordance with reviewer recommendations.  A complete and detailed account of the revisions is included below.  The reviewer comments were very helpful, much appreciated, and have resulted in a better manuscript.  In addition to submitting a revised version of the manuscript incorporating the latest changes, we are also submitting production quality images.

\vspace{2em}

Much appreciated, \newline

\vspace{1em}

Denis S. Willett
\vspace{0.48em}

Camila C. Filgueiras
\vspace{0.48em}

Jan P. Nyrop
\vspace{0.48em}

Brian A. Nault
\vspace{0.48em}

\vspace{1.4em}

\hline

\setlength\parindent{0pt}

\subsection*{Reviewer 1}

Well-written paper.  I feel the research is new, important and relevant to the industry.  The methods and statistical analysis are appropriate.  I agree with the reported results; a few of the discussion points seem to go a little too far from the scope of research and are not supported with data or referenced material.

\begin{quote}
    \textit{Thank you for reviewing the paper.  We appreciate your comments and concise summary.  We've adjusted the language in accordance with your suggestions and refined discussion points to not expand beyond the scope of research.  }
\end{quote}

One concern is it appears some of the studies may not have been replicated in space or time.  It is stated trials were conducted in 2005 and 2006 but some studies only have 4-5 raw data points and no reported year effects in Table 1.  Please clarify which studies were replicated in space and time.   Below are comments referenced by line number.

\begin{quote}
    \textit{Thanks for your inquiry.  All trials were replicated in space.  Not all trials had year effects; size trials were replicated across years.  It should be noted that the trials were iterative in the sense that improvement decisions were made and incorporated into subsequent trials.  }
\end{quote}

Line 10-12- Consider revising sentence.  Current cultural management especially altering planting date, field location, and crop rotation depend on monitoring.

\begin{quote}
    \textit{Thanks for suggesting this.  We have included your suggestions in the updated version of the paper.  }
\end{quote}

Line 75-76- Were all studies conducted in 2005 and 2006 or just some trials? Please clarify.

\begin{quote}
    \textit{Thanks for your inquiry - please see comments above.}
\end{quote}

Line 88-90- It would be helpful to know what insecticides were applied to the fields during the monitoring period (Late May to Late June) if information is available?

\begin{quote}
    \textit{Great question - The management program almost identically followed the proposals put forth by Reiners et al., 2019. } 
\end{quote}

Line 106- Why wasn't blue used in the study if other studies indicated it attracted \textit{D. antiqua} flies.

\begin{quote}
    \textit{Excellent question - blue wasn't used in this trial because we simply did not imagine that blue would be an attractive color.  The results suggesting that blue could be attractive were published in 2018 - well after we completed this study.  It should be noted that there could be a trade off with use of blue traps however.  While specificity for onion maggot seems higher on blue traps, overall catch numbers suffer. 
    }
\end{quote}

Line 138- Is it necessary to spell out P-values and R2 values when cited in Table 1 for all result sections.  Recommend either referring to Table 1 and leaving out text.

\begin{quote}
    \textit{Thanks for your suggestion.  We've removed the redundancy and just cited Table 1 in the text.  }
\end{quote}

Line 143- "short cylinders numerically caught "X" more females  then cubes and spheres.

\begin{quote}
    \textit{Excellent suggestion.  We've added this additional information in the text.}
\end{quote}

Line 145- This is probably outside the scope of the study but did the larger trap sizes also correspond to capture of more non-target insects?  Did larger traps require additional support to prevent movement in wind?

\begin{quote}
    \textit{Great questions.  While this is somewhat outside the scope of the paper, larger sizes had more insects, but we did not look into quantifying non-targets.  Larger traps did not require much in the form of additional supports for the wind.  The only challenging part of supporting traps was actually the deer population.  At one of our sites, particularly hungry deer devoured our spheres. Must have been pretty hungry put up with the taste.  }
\end{quote}

Line 185- Again, why wasn't blue tested in the study?

\begin{quote}
    \textit{Excellent question.  See previous response}
\end{quote}

Line 202- change "has reduced"

\begin{quote}
    \textit{Thanks for catching this typo.  We have corrected it in the updated version of the manuscript.}
\end{quote}

Line 210-212- This statement is not supported by data nor referenced materials.  The number of flies captured in all treatments is small.  It seems unlikely the number of captured adults even with several traps per field would reduced the overall population enough to influence maggot damage.  It might be worth citing research investigating insecticide applications targeting adults used in combination with trapping and how they influence onion maggot fly populations and onion maggot damage to provide context to other statements in the final paragraph.

\begin{quote}
    \textit{Good point.  We may have gotten ahead of ourselves in discussing future work and upcoming results.  This will have to wait for the next manuscript.  We have adjusted the language towards the end of the discussion to capture the results of the paper and better rely on current literature support.  }
\end{quote}

\subsection*{Reviewer 2}

The authors report on field tests, using different types of traps (shape, colour, baits) aiming at improving catches of onion flies. While I don’t question the importance of improving a trap design to base control measures on the occurrence of these flies in the onion fields I doubt that the authors would be able to contribute to phenological modelling approaches by using these data. No information is provided on the background populations of onion flies in these fields or the damage levels. The authors state that improved traps create the “opportunity for a different, more environmentally friendly, management method”.  Overall, the discussion section is only marginally developed and there are many additional opportunities to refer and discuss studies on maggot flies, carrot flies, or cabbage flies. The whole section on the Attract & Kill approach is not reflecting the state of the art discussion.

\begin{quote}
    \textit{Thank you for your concise summary and for reviewing the paper.  We appreciate your comments and have endeavored to incorporate your suggestions in the revised manuscript.  We have elaborated upon work on other flies and have removed discussion of the Attract and Kill approach while focusing on its contribution to an integrated pest management approach.  }
\end{quote}

Misc.:
25 correct citations throughout the MS: Nault, Straub….-  not B. A. Nault….

\begin{quote}
    \textit{Thank you for pointing this out.  The citations in the version rendered in Word turned out a bit odd.  The citations are correct in the LaTeX version assembled using the JAE template that will be used for publication. }
\end{quote}

29 would be interesting for the reader to learn details about which compounds are involved

\begin{quote}
    \textit{Thanks for your suggestion.  Details about developing resistance are elaborated upon in the cited papers. }
\end{quote}

37 … generations and plant pathogens

\begin{quote}
    \textit{Thanks for the opportunity to clarify.  This has been updated in the revised version of the paper.  }
\end{quote}

49 give reason why insecticide application is not desired – organic production?

\begin{quote}
    \textit{Excellent suggestion to clarify.  It has been adjusted in the revised version of the manuscript. }
\end{quote}

63 (and 70, 182, 186, 299) is this report accessible to readers? Guess not; thus it should not be cited;

\begin{quote}
    \textit{Thanks for your inquiry.  This report is accessible to readers and the general public; it is not behind a pay wall.  For some reason, Word rendered the formatting wrong.  The LaTeX version with the JAE template has the full information including an accessible url for public perusal.  }
\end{quote}

76 why data from 2005 and 2006; seems a bit outdated!

\begin{quote}
    \textit{Excellent question.  While the trials were conducted in 2005 and 2006, renewed interest in alternative management options for onion maggot in New York has prompted us to put together this paper. We feel this is useful information that serves as a base for future work in the pipeline documenting effective onion maggot management using the trap development documented here.  }
\end{quote}

80ff the layout of the traps within the fields is not sufficiently outlined in detail. The position of the traps was most probably within the fields; however, adjacent fields and the incidence of surrounding onion field may have had an influence on trap catches as well. What about wind direction? Do onion flies have rendezvous-places (at least known from Delia platura)?  What means “long edge of an onion … field”?  
\begin{quote}
    \textit{Thanks for your suggestion.  We have elaborated on trap location to some extent in the text.  GPS coordinates of trap locations are also available upon request.  We did not control for nor record wind direction.  \textit{D. antiqua} does have rendezvous places; catch seems to be higher along edges of fields hence the trap placement.  The onion fields are rectangular with the long edge being the longer of the pairs of sides.  }
\end{quote}

92 Why were traps placed at a distance of 15.2 m? Sounds a bit odd! Has this distance been evaluated for interactions? How did time influence trap catches; seems that the traps were exposed for 4 weeks; any differences in trap dynamics for the different types tested?

\begin{quote}
    \textit{Excellent question.  Because our growers work with standard measurements, 50 feet (the 15.2m equivalent) divides up the field nicely and uniformly.  This distance was additionally chosen because we believe that it is much larger than would cause interactions.  We did not see much variation in trap dynamics over time for the designs tested.  
    }
\end{quote}

152 what is meant with trend? This is not a statistically resilient term – significant or not significant!

\begin{quote}
    \textit{Excellent question.  This is actually a statistical term and there are numerous types of trend analysis.  In linear trend analysis (the case here) trend is essentially slope and can be fitted using the least squares method.  In analysis with sizes, diameter can be treated as either a categorical (the case in our paper) or continuous variable.  In the continuous case, the trend would be the slope of the relationship between size and trap catch and the coefficient of this term in the linear model.  Trends were similar in our studies because as trap sphere diameter increased, trap catch also increased for both males and females.  This is an important applied point because there seems to be little difference between the sexes.  We did not dive further into trend analysis nor pursue the continuous analysis approach because we felt that display of the categorical approach would be more intuitive for management professionals and because identification of the scaling factor for continuity would require further research to disentangle which is more important: diameter, volume, or surface area.  
    }
\end{quote}

204 I doubt that a mass trapping approach would result in control of these flies. Flies may be attracted to these traps from adjacent fields or landscapes, thus high trap catches may not reflect the real population densities. Are data available which clearly demonstrate that increasing catches in one field reduce onion damage?

\begin{quote}
    \textit{Great question.  This point also relates to your inquiry regarding the relevance of publishing data from 2005 and 2006.  More recent work using the results related report on the efficacy of using this approach to reduce onion damage in the field.  }
\end{quote}

Figures: It is a bit strange that the CVs of the males are always much lower than those of the females – this should be discussed. Are females better dispersers? Do the traps attract males or do males seek for females?

\begin{quote}
    \textit{Thanks for your inquiry.  The male catch is always less than females.  We have elaborated upon this in the discussion.  }
\end{quote}

Figures 4: Delia Lure trials have been made 3 times with 4 reps per treatment; however, the figures shows 6 symbols – please explain why 6 and which are solid and shaded points – not visible in the PDF file

\begin{quote}
    \textit{Thanks for mentioning this.  We have clarified in the figure description.  In this case the points are not the raw values (text copied from previous figures), but rather replicate totals.  Your math is correct with the additional consideration that this trial was conducted in two fields bringing the grand total to 3x4x2 = 24.  }
\end{quote}

\end{document}

### 2020-01-06 manuscript/pest-management-science/reviewer-response/reviewer-response.tex

\vspace{1.24em}

Dear Dr. Torto,

\vspace{0.48em}
\setlength{\parindent}{1.24cm}

Thank you for your consideration of \textit{“Attract and kill: Spinosad containing spheres to control onion maggot (\textit{Delia antiqua})”} for publication in Pest Management Science.  We have revised the manuscript in accordance with reviewer recommendations.  A complete and detailed account of the revisions is included below.  The reviewer comments were very helpful, much appreciated, and have resulted in a better manuscript.  In addition to submitting a revised version of the manuscript incorporating the latest changes, we are also submitting production quality images.

@@

\vspace{1.4em}

\hline

\setlength\parindent{0pt}

\subsection*{Referee 1}

The authors did a great job writing the manuscript.  The introduction, methods, and results were easy to understand.

\begin{quote}
    \textit{Thank you for reading the manuscript and providing constructive feedback.  We appreciate the suggestions and have endeavored to include them in the revised version.  }
\end{quote}

On lines 54 and 55 the authors state field trials were conducted from 2006 to 2008, but they did NOT describe if all experiments were repeated in 2006, 2007, and 2008.  The authors need to describe which experiments were conducted each year, how many times each experiment was replicated, and if the experiments were replicated in space and time.

\begin{quote}
    \textit{Thanks for the opportunity to clarify.  Details on the timing of trials are now included in at the beginning of each sub-section in the Material and Methods section on lines ....  In short, the trials were replicated in space and time.  }
\end{quote}

The authors should add a few sentences describing the field sites (lines 54-56) cropping history (e.g. Where onions grown in previous years?) and the reason why the fields were chosen (e.g. did the fields have a previous history of onion maggot damage?).  If experiments were not replicated in space or time it should be noted in the Material and Methods.

\begin{quote}
    \textit{Thanks for mentioning this opportunity to elaborate.  Details on cropping history and reasoning behind field site choice have now been included on lines ....  Information on how experiments were replicated in space and time are also included (see above).  }
\end{quote}

In the discussion section the authors made no mention of using spinosad seed treatment as a management option in conventional and organic onion fields.  Why?? Spinosad (Regard) seed treatment is currently the primary management method for onion maggot in organic onions, and spinosad is an active ingredient in many conventional seed treatments.   Spinosad is an active ingredient in the FI500 seed treatment, and Regard alone often provides a similar level of protection compared to FI500.  Since FI500 resulted in lower maggot damage compared to all "attract and kill" tactics, why would someone recommend attract and kill with spinosad over spinosad seed treatment?   I strongly recommend the authors discuss the advantages, disadvantages, and compatibility of using spinosad seed treatment and spinosad attract & kill.

The authors should discuss the implications of onion maggot developing resistance to spinosad using the attract and kill tactic.  e.g. Will the attract and kill tactic with spinosad lead to a higher likelihood of onion maggot developing resistance to spinosad?  This tactic targets egg laying adults, it only provides partial control, and it exposes multiple generations per year to spinosad?   These factors seem to favor resistance. This question is especially relevant as the most popular registered insecticide seed treatments contain spinosad and there are few alternatives in the marketplace.

\subsection*{Referee 2}

The methods and results need some significant improvements. I found that methods lacking in details and the analysis not well described. I also noted in the annotated file that the quality of the writing in the intro and discussion is markedly different and will need some work to bring them to the same level.

\begin{quote}
    \textit{Thank you for your comments regarding the manuscript.  We have added extended details to the methods section describing both the field work and analysis.  Additionally, we have adjusted language in the introduction and discussion.  We appreciate your feedback in helping improve the manuscript.  }
\end{quote}

Line 60: Please check and correct.

\begin{quote}
    \textit{Thanks for the opportunity to verify this.  It is correct.  'Abut' (spelled exactly that way) means to share a common border. }
\end{quote}

Line 63: Not sure why its assumed that color and rate are related, explain.

\begin{quote}
    \textit{Interesting question.  There is no assumption that color and rate are related.  The fact that white spheres are attractive to \textit{D. antiqua} is based on previous research in this system.  }
\end{quote}

Line 65: Does this sentence belong to the next paragraph? move it there.

\begin{quote}
    \textit{Excellent suggestion.  This sentence does seem to be hanging there.  Rather than include it in the subsequent paragraph, we have opted to remove it alltogether.  }
\end{quote}

Line 66: be more specific.

\begin{quote}
    \textit{Thanks for the opportunity to elaborate.  We have included more details as to the timing and location of the trials throughout the methods section, specifically lines .... }
\end{quote}

Line 68: climate or weather?

\begin{quote}
    \textit{Interesting question.  We want to use the weather in these trials as a proxy for general exposure to northern climates and have revised the sentence in accordance with your suggestion.  }
\end{quote}

Line 68-69: This was already state above, seems redundant.

\begin{quote}
    \textit{Thanks for mentioning this.  We have removed the redundant statement.  }
\end{quote}

Line 71: More details are needed: how many reps/field, how many fields, how much distance between spheres, etc. Where in the field relative to the crop were spheres? What were they placed on and how high?

\begin{quote}
    \textit{}
\end{quote}

Line 77: Which years was this experiment done? Throughout this section pls change to using SI units.

Line 91: was this based on a preliminary experiment?

Line 99: novel? How was it different from previously used ones?

Line 100: why were these compounds chosen?
\end{document}

### 2020-01-06 manuscript/pest-management-science/main.tex
prep for revisions
adding to reviewer revisions

Field trials evaluating the efficacy of attract and kill strategies to manage \textit{D. antiqua} populations were conducted from 2006 to 2008 in commercial dry bulb onion fields on muck soils in upstate New York, USA.  Muck soils are high organic matter soils formed from old lake beds.  Trials were conducted from May to September.

@@

Population monitoring of \textit{D. antiqua} adults was accomplished by deploying white sticky cards in triplicate along onion field edges in each of six commercial onion fields.  Field edges have been identified as ideal locations for trapping adult fly populations, especially when borders abut woodlands \citep{werling2006spatial}.  Cards were collected weekly from May to September and the number of male and female adult flies counted.

@@

To do so, the ability of spinosad spheres to kill \textit{D. antiqua} flies was evaluated over the course of multiple field seasons by deploying a cohort of spheres containing spinosad at the beginning of the season (mid May) and recovering a subset of them on a monthly basis to evaluate climate and dose effects. Spheres had three levels of spinosad: No spinosad (Control), 0.5\% spinosad, and 1\% spinosad. Following initial deployment in mid May spheres were recovered in mid June, mid July, mid August, and mid September resulting in cohorts exposed to field conditions for 1 month, 2 months, 3 months, 4 months, respectively. Deployment in the field followed a randomized controlled block design.

@@

To evaluate the efficacy of attract and kill techniques for reducing \textit{D. antiqua} larval damage, onions killed or damaged by \textit{D. antiqua} larvae were monitored throughout the season. Onion seed of \textit{Allium cepa} L. ’Arsenal’, an early yellow globe variety, was planted in late April with plants subjected to six treatments in a randomized controlled block design. Insecticide-treated plants were grown from seeds treated with the FarMore FI500 seed treatment package. This treatment was included in the experiment to be a positive control. Non-insecticide treated plants were grown from fungicide-only treated seeds and did not receive any attract and kill strategies. Spinosad spheres containing 0.5\% spinosad were deployed with and without attractive Delia Lures (AgBio, Westminster, CO) as an attract and kill solution. White sticky cards with and without attractive Delia Lure were also deployed. Four replications of each of the six treatment combinations were evaluated (i.e., insecticide-treated plants only [positive control], non-insecticide treated plants with spinosad containing white spheres only, non-insecticide treated plants with spinosad containing white spheres and Delia Lure, non-insecticide treated plants with white sticky cards only, non-insecticide treated plants with white sticky cards and Delia Lure, and non-insecticide treated plants only [negative control]).

Each individual experimental plot was 8 rows by 30 feet long separated from its nearest neighboring experimental plot by a minimum of 100 feet in any direction. Three weeks following planting, seedlings in the middle two rows were counted to obtain an initial stand count. Following initial stand count, plant loss due to damage by \textit{D. antiqua} larvae was evaluated on a weekly basis in the middle two rows until the end of season when a final stand count was taken (including all mortality factors). Plants killed by \textit{D. antiqua} were assessed visually, then confirmed by removing the plant and ascertaining presence of \textit{D. antiqua} larvae. When plants became too large to visually detect \textit{D. antiqua} damage, subsamples of plants were removed from the soil and bulbs inspected for \textit{D. antiqua} larvae and larval feeding damage. The overall percentage of cumulative \textit{D. antiqua} damaged plants for the season was determined.

@@

To enhance attractiveness, longevity, and performance of spinosad containing spheres, a new formulation of spinosad containing sphere was developed with 0.5\% spinosad, 5.0\% ammonium carbonate and 5.0\% casein hydrolysate. The efficacy of this new formulation was compared with spheres containing just 0.5\% spinosad and no spinosad controls in field cage trials. Treatments were deployed in a randomized controlled block design with four replications and each individual plot consisted of four rows of onion each 3.7m (12ft)  long. All onion seeds including those in the untreated control were treated with fungicides: thiram (Thiram 42 S {@}188 mg a.i./ 100 g seed) and tebuconazole (Raxil 2.6 F @ 250 mg a.i. / 100 g seed). Seeds were planted in early May and each plot was caged (3.7m x 3.7m x 2m) using PVC pipe and screen mesh. One hundred fifty \textit{D. antiqua} flies with a 50:50 male to female ratio were released into each cage on the second of June and again nine days later on June 11th. As described above, initial and final stand counts were taken and plant damage due to \textit{D. antiqua} larvae evaluated on a weekly basis.

@@

\graphicalabstract{example-image-1x1}{Please check the journal's author guildines for whether a graphical abstract, key points, new findings, or other items are required for display in the Table of Contents.}

>>>>

Field trials evaluating the efficacy of attract and kill strategies to manage \textit{D. antiqua} populations were conducted from 2006 to 2008 in commercial dry bulb onion fields on muck soils in upstate New York, USA.  Muck soils are high organic matter soils formed from old lake beds.  Trials were conducted from May to September.  All field sites used in these trials had a history of continuous onion production, had historically relatively prominent \textit{D. antiqua} populations, and grower collaborators interested in improving management.

@@

Population monitoring of \textit{D. antiqua} adults was accomplished in 2006 by deploying white sticky cards in triplicate along onion field edges in each of six commercial onion fields.  Field edges have been identified as ideal locations for trapping adult fly populations, especially when borders abut woodlands \citep{werling2006spatial}.  Cards were collected weekly from May to September and the number of male and female adult flies counted.

@@

To do so, the ability of spinosad spheres to kill \textit{D. antiqua} flies was evaluated over the course of 2006 and 2007 field seasons by deploying a cohort of spheres containing spinosad at the beginning of the season (mid May) and recovering a subset of them on a monthly basis to evaluate weather exposure and dose effects.  Following initial deployment in mid May spheres were recovered in mid June, mid July, mid August, and mid September resulting in cohorts exposed to field conditions for 1 month, 2 months, 3 months, 4 months, respectively. Deployment in the field followed a randomized controlled block design.

@@

To evaluate the efficacy of attract and kill techniques for reducing \textit{D. antiqua} larval damage, onions killed or damaged by \textit{D. antiqua} larvae were monitored throughout the field seasons of 2007 and 2008. Onion seed of \textit{Allium cepa} L. ’Arsenal’, an early yellow globe variety, was planted in late April with plants subjected to treatments in a randomized controlled block design with six replicates across three field sites.  Six treatment combinations were evaluated (i.e., insecticide-treated plants only [positive control], non-insecticide treated plants with spinosad containing white spheres only, non-insecticide treated plants with spinosad containing white spheres and Delia Lure, non-insecticide treated plants with white sticky cards only, non-insecticide treated plants with white sticky cards and Delia Lure, and non-insecticide treated plants only [negative control]).  Insecticide-treated plants were grown from seeds treated with the FarMore FI500 seed treatment package. This treatment was included in the experiment to be a positive control. Non-insecticide treated plants were grown from fungicide-only treated seeds and did not receive any attract and kill strategies. Spinosad spheres containing 0.5\% spinosad were deployed with and without attractive Delia Lures (AgBio, Westminster, CO) as an attract and kill solution. White sticky cards with and without attractive Delia Lure were also deployed.

Each individual experimental plot was 8 rows by 9.1m  long separated from its nearest neighboring experimental plot by a minimum of 30.5m  in any direction. Three weeks following planting, seedlings in the middle two rows were counted to obtain an initial stand count. Following initial stand count, plant loss due to damage by \textit{D. antiqua} larvae was evaluated on a weekly basis in the middle two rows until the end of season when a final stand count was taken (including all mortality factors). Plants killed by \textit{D. antiqua} were assessed visually, then confirmed by removing the plant and ascertaining presence of \textit{D. antiqua} larvae. When plants became too large to visually detect \textit{D. antiqua} damage, subsamples of plants were removed from the soil and bulbs inspected for \textit{D. antiqua} larvae and larval feeding damage. The overall percentage of cumulative \textit{D. antiqua} damaged plants for the season was determined.

@@

To enhance attractiveness, longevity, and performance of spinosad containing spheres, a new formulation of spinosad containing sphere was developed with 0.5\% spinosad, 5.0\% ammonium carbonate and 5.0\% casein hydrolysate. The efficacy of this new formulation was compared with spheres containing just 0.5\% spinosad and no spinosad controls in field cage trials in 2008. Treatments were deployed in a randomized controlled block design with four replications and each individual plot consisted of four rows of onion each 3.7m (12ft)  long. All onion seeds including those in the untreated control were treated with fungicides: thiram (Thiram 42 S {@}188 mg a.i./ 100 g seed) and tebuconazole (Raxil 2.6 F @ 250 mg a.i. / 100 g seed). Seeds were planted in early May and each plot was caged (3.7m x 3.7m x 2m) using PVC pipe and screen mesh. One hundred fifty \textit{D. antiqua} flies with a 50:50 male to female ratio were released into each cage on the second of June and again nine days later on June 11th. As described above, initial and final stand counts were taken and plant damage due to \textit{D. antiqua} larvae evaluated on a weekly basis.

@@

%\graphicalabstract{example-image-1x1}{Please check the journal's author guildines for whether a graphical abstract, key points, new findings, or other items are required for display in the Table of Contents.}
